SMASH companion source code repository

### 2021-06-25 analysis/index.Rmd
workflowr::wflow_publish("index.Rmd")
workflowr::wflow_publish("analysis/index.Rmd")

> Zhengrong Xing, Peter Carbonetto and Matthew Stephens (2021).
> [Flexible signal denoising via flexible empirical Bayes shrinkage.][smash-jmlr]
> *Journal of Machine Learning Research* 22(93), 1-28.

@@

The following analyses generate some of the empirical results
presented in [Xing, Carbonetto & Stephens (2020)][smash-preprint]. If
you encounter a problem running any of the R code in these examples,
please post an [issue][issues].

>>>>

> Zhengrong Xing, Peter Carbonetto and Matthew Stephens (2021).
> [Flexible signal denoising via flexible empirical Bayes shrinkage.][smash-jmlr]
> *Journal of Machine Learning Research* 22(93), 1--28.

@@

The following analyses generate some of the empirical results
presented in [Xing, Carbonetto & Stephens (2020)][smash-jmlr]. If
you encounter a problem running any of the R code in these examples,
please post an [issue][issues].
